### 2016-12-08 radio/equation.hetero.tex
課題7

\frac{1}{8} (A^2 m^2 {\rm cos}(2 \omega - 2 \omega_1) + A^2 m^2 {\rm cos}(2 \omega + 2 \omega_1) - 4 A^2 m {\rm sin}(\omega - 2 \omega_1) - 4 A^2 m {\rm sin}(\omega + 2 \omega_1) - 2 A^2 m^2 {\rm cos}(2 \omega) + 8 A^2 m {\rm sin}(\omega) + 4 A m {\rm sin}(2 \omega - \omega_1 + \omega_m) - 4 A m {\rm sin}(2 \omega + \omega_1 + \omega_m) + 8 A {\rm cos}(\omega - \omega_1 + \omega_m) - 8 A {\rm cos}(\omega + \omega_1 + \omega_m) - 4 {\rm cos}(2 \omega + 2 \omega_m) - 2 A^2 m^2 {\rm cos}(2 \omega_1) - 4 A^2 {\rm cos}(2 \omega_1) + 2 A^2 m^2 + 4 A^2 + 4 A m {\rm sin}(\omega_1 - \omega_m) + 4 A m {\rm sin}(\omega_1 + \omega_m) + 4)